Universal Anonymous Signatures

### 2022-07-10 prism-backend/research/gsac/formal-uas.tex
Defining Extract* and Identify* properties.

\begin{description}
\item[$\fissue: (\usk,\scred,\attrs)
  \rightarrow 0/1$.] Chosen by each issuer within a family of functions
  \famfissue, the issuance function defines the customized conditions required
  by the issuer to grant a credential over attributes \attrs, when requested by
  a user with secret key \usk, potentially leveraging a set of previously
  obtained credentials \scred. \fissue returns $1$ to accept a request, $0$ to
  reject it.
\item[$\feval: (\usk,\scred,\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user secret key \usk, credentials \scred, and message to be signed
  \msg. \feval outputs two values, $\yeval^0$ and $\yeval^1$, where the former
  is revealed in plaintext along with the signature, and $\yeval^1$ is
  encrypted. Both can be used to modulate the bevahiour of \finsp, and must
  belong in a well defined set \rngfeval. For readability, we write $\Yeval =
  (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\usk,\scred,\msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value, derived from the user's secret key,
  credentials used for signing, and signed message, should be extractable by an
  opener. Its behaviour can be modulated by \Yeval, and it outputs a value
  \yinsp, which must belong in a well defined set \rngfinsp.
\end{description}

@@

\paragraph{Helper functions \SimSetup, \ExtractIssue, \ExtractSign,
  \IdentifyCred, and \IdentifyUK.} We assume the existence of these helper
functions. They are not functions available in the actual scheme, but rather to
the challenger in the experiments we use to formalize security of \UAS schemes.
Consequently, while we introduce them here and specify some conditions they need
to meet, their full definition is dependent on the construction. We fully define
them for our generic construction \CUASGen in \appref{app:uas-proofs}. Similar
techniques have been used before to prove security in privacy-preserving schemes
with some sort of accountability, but that do not offer conventional opening as
vanilla group signatures. For instance, see related works on DAA
\cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}.
More concretely, these functions are as follows:

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global (simulated) parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
  and returns the credentials (if any) and their attributes involved in the
  request. It needs an honest issuer as, otherwise, the transcripts won't be
  available. 
\item[$\ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a
  signature \Sig,
  as well as the opener identifier \oid, and the identifiers of all issuers of
  the credentials used to produce the signature over \msg, and for \feval.
  It outputs the user secret key and credentials (with their attributes) used to
  generate the signature, and the $\yeval^1$ and \yinsp values.
\item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
  Otherwise, it returns $0$. In order to be meaningful, this requires that,
  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
  \IdentifyCred return $1$.
\item[$\IdentifyUK(\trap,\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret
  key. This is trivial for honest users, for which there must be a one-to-one
  relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
  to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
  to \uid, extract the used secret key, and check if there is a match. In the
  latter case, there is no guarantee of getting a one-to-one relationship
  between \usk and \uid. Also, when used for corrupt users, this can only be
  used when the issuer is honest, as transcripts are needed. 
\end{description}

@@

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      \cid \gets \adv^{\Oforgeissue}(\parm) \\
      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
      \exists \cred \in \scred~\suchthat~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
  \label{fig:exp-uas-unfor-issue}
\end{figure}

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
      (\parm,\trap) \gets \Setup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0: \pcreturn 1 \\
      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets
      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1
      \lor \Yeval \notin \rngfeval:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp'
      \lor \yinsp \neq \yinsp':
      \pcreturn 1 \\
      \pcif \exists \cred \in \scred~\suchthat~
      \IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
      \pcreturn 1 \\
      \pcif \nexists \uid~\suchthat~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
    (\parm,\trap) \gets \SimSetup(1^\secpar) \\
    (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
    \pcreturn 0 \\
    \pcif \exists (\cdot,\cdot,\Sig,\Yeval,\msg,\feval)
    \in \SIG[\uid]: \pcreturn 0 \\    
    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
    \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1
    \lor \Yeval \notin \rngfeval: \pcreturn 1 \\
    \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
    \lor \yinsp \neq \yinsp': \pcreturn 1 \\    
    \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}

>>>>

\begin{description}
\item[$\fissue: (\usk,\attrs_{\scred},\attrs)
  \rightarrow 0/1$.] Chosen by each issuer within a family of functions
  \famfissue, the issuance function defines the customized conditions required
  by the issuer to grant a credential over attributes \attrs, when requested by
  a user with secret key \usk, potentially leveraging a set of previously
  obtained credentials with attributes $\attrs_\scred$. \fissue returns $1$ to
  accept a request, $0$ to reject it.
\item[$\feval: (\usk,\attrs_{\scred},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user secret key \usk, a set $\attrs_{\scred}$ of attributes in the
  credenetial used for signing, and message to be signed
  \msg. \feval outputs two values, $\yeval^0$ and $\yeval^1$, where the former
  is revealed in plaintext along with the signature, and $\yeval^1$ is
  encrypted. Both can be used to modulate the bevahiour of \finsp, and must
  belong in a well defined set \rngfeval. For readability, we write $\Yeval =
  (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\usk,\attrs_{\scred},\msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value, derived from the user's secret key,
  credentials used for signing, and signed message, should be extractable by an
  opener. Its behaviour can be modulated by \Yeval, and it outputs a value
  \yinsp, which must belong in a well defined set \rngfinsp.
\end{description}

@@

\paragraph{Helper functions \SimSetup, \ExtractIssue, \ExtractSign,
  \IdentifyCred, and \IdentifySig.} We assume the existence of these helper
functions. They are not functions available in the actual scheme, but rather to
the challenger in the experiments we use to formalize security of \UAS schemes.
Consequently, while we introduce them here and specify some conditions they need
to meet, their full definition is dependent on the construction. We fully define
them for our generic construction \CUASGen in \appref{app:uas-proofs}. Similar
techniques have been used before to prove security in privacy-preserving schemes
with some sort of accountability, but that do not offer conventional opening as
vanilla group signatures. For instance, see related works on DAA
\cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}.
More concretely, these functions are as follows:

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global (simulated) parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
  and returns the credentials (if any) and their attributes involved in the
  request. It needs an honest issuer as, otherwise, the transcripts won't be
  available. 
\item[$\ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a
  signature \Sig,
  as well as the opener identifier \oid, and the identifiers of all issuers of
  the credentials used to produce the signature over \msg, and for \feval.
  It outputs the user secret key and credentials (with their attributes) used to
  generate the signature, and the $\yeval^1$ and \yinsp values.
\item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
  \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
  secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
  $0$.

  The \IdentifyCred function defined by \UAS constructions must satisfy that
  for any \cred obtained as the result of an $\langle \Obtain,\Issue \rangle$
  interaction with an honest issuer, there exists \emph{exactly one} set of
  $(\usk,\attrs_{\cred})$ such that \IdentifyCred equals $1$.
  %In order to be meaningful, this requires that,
  %for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
  \IdentifyCred return $1$.
\item[$\IdentifySig(\trap,\usk,\scred,\Sig)$.] Returns $1$ is $(\usk,\scred)$
  are the secret key and credential set used to produce \Sig, otherwise, returns
  $0$.

  The \IdentifySig function defined by \UAS constructions must satisfy that, for
  signatures accepted by \Verify, there must exist \emph{exactly one} $(\usk,
  \scred)$ combination that makes \IdentifySig return $1$.
  % . This is trivial for honest users, for which there must be a one-to-one
  % relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
  % to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
  % to \uid, extract the used secret key, and check if there is a match. In the
  % latter case, there is no guarantee of getting a one-to-one relationship
  % between \usk and \uid. Also, when used for corrupt users, this can only be
  % used when the issuer is honest, as transcripts are needed. 
\end{description}

@@

Security of an \UAS scheme is defined in terms of anonymity, unforgeability and
non-frameability. Where the first two have variants covering issuance and
signatures \todo{argue why issuance non-frameability does not make sense}.
%
However, as stated, we make use of some helper functions: \ExtractIssue and
\ExtractSign, which let us recover the witnesses used to produce a credential
or a signautre; and \IdentifyCred, and \IdentifySig, which associate credentials
and signatures to user identifiers \uid. Both types of functions have been used
before. For instance, the extraction-type are used in \cite{lnpy21,nps22}, and
functions of the identify-type are used in \cite{bfg+11,cdl16,gl19,dl21,fgl21}.
\todo{Re-write after done.} Indeed, it seems hard to avoid resorting to these
techniques when there is no traditional notion of opening.

\paragraph{Extractability.} %
We require that the witnesses used to produce each credential and signature can
be extracted from the corresponding \utrans and signature, respectively.
Furthermore, in order for our generalized notion of utility to have meaning, it
is required that, whenever a credential is issued by an honest issuer, or a
signature is accepted by \Verify, the extracted values produce the same value as
the chosen \fissue, \feval and \finsp functions. We capture this in the
\ExpExtractIssue and \ExpExtractSign games, which are crucial in the
unforgeability and non-frameability requirements.

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering]{$\ExpExtractIssue(1^\secpar)$}{%
        (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\todo{\OExtIss}}(\parm) \\
        (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
    \vspace*{0.5em}

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpExtractSign(1^\secpar)$}{%
        (\parm, \trap) \gets \SimSetup(1^\secpar) \\
	(\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets
        \adv^{\todo{\OExtSig}}(\parm) \\
	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
	(\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \gets        
        \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
        \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
        \pcreturn 1 \\
        \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
        \pcreturn 1 \\
	\pcreturn 0
      }
    \end{minipage}
  }
  \caption{Extractability experiments for \UAS schemes.}
  \label{fig:exp-uas-extract}
\end{figure*}

\paragraph{Identifiability.} %
On their own, the extractability properties only ensure that the produced
credentials and signatures have been produced by leveraging knowledge of some
witnesses. However, they do not establish any relationship between those
witnesses and the identity of their owner(s). While the way in which witnesses
are associated to user identifiers\footnote{We avoid the term \emph{user
    identity}, as that is very context-specific.} is dependent on the
construction, we impose some constraints that all schemes need to satisfy.
Namely, it must be possible to associate any credential (obtained from an honest
issuer), or any signature accepted by \Verify, to exactly one user identifier.

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering]{$\ExpIdentifyCred(1^\secpar)$}{%
        (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\todo{\OIdCred}}(\parm) \\
        (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        \suid \gets \IdentifyCred(\trap,\usk,\scred,\attrs_{\scred},\ipk_{\cred}) \\
        \pcif |\suid| \neq 1: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
    \vspace*{0.5em}

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpIdentifySign(1^\secpar)$}{%
        (\parm, \trap) \gets \SimSetup(1^\secpar) \\
	(\oid,\siid,\Sig,\msg,\feval) \gets \adv^{\todo{\OIdSig}}(\parm) \\
	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
	(\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \gets
        \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
	\suid \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
	\pcif |\suid| \neq 1: \pcreturn 1 \\
	\pcreturn 0
      }
    \end{minipage}
  }
  \caption{Identifiability experiments for \UAS schemes.}
  \label{fig:exp-uas-identify}
\end{figure*}

\begin{definition}{(Identifiable credentials in \UAS)}
  \label{def:identify-cred-uas}  
  We define the advantage \AdvIdCred of $\adv$ against \ExpIdentifyCred as
  $\AdvIdCred=|\Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies identifiable credentials if, for any p.p.t. adversary
  $\adv$, \AdvIdentifyCred is a negligible function of $1^\secpar$.
\end{definition}

\begin{definition}{(Identifiable signatures in \UAS)}
  \label{def:identify-sig-uas}  
  We define the advantage \AdvIdSig of $\adv$ against \ExpIdentifySign as
  $\AdvIdSig=|\Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies identifiable signature if, for any p.p.t. adversary
  $\adv$, \AdvIdSig is a negligible function of $1^\secpar$.
\end{definition}

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      \cid \gets \adv^{\Oforgeissue}(\parm) \\
      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
      \exists \cred \in \scred~\suchthat~\IdentifyCred(\trap,\usk,
      \attrs_{\cred},\cred,\ipk) = 0: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
  \label{fig:exp-uas-unfor-issue}
\end{figure}

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
      (\parm,\trap) \gets \Setup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0: \pcreturn 1 \\
      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets
      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
      \pcreturn 1 \\
      \pcif \exists \cred \in \scred~\suchthat~
      \IdentifyCred(\tau,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) = 0:
      \pcreturn 1 \\
      \pcif \nexists \uid~\suchthat~\IdentifySig(\trap,\usk,\scred,\Sig) = 1:
      \pcreturn 1 \pccomment{\todo{\uid-\usk}} \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}

@@

\begin{figure}[htp!]
  \centering
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
    (\parm,\trap) \gets \SimSetup(1^\secpar) \\
    (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
    \pcreturn 0 \\
    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
    \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
    \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
    \lor \yinsp \neq \yinsp': \pcreturn 1 \\   
    \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk \land
    (\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\uid]: \\
    \pcind \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}
